Condensed Matter Field Theory notes

### 2017-03-08 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] notes about Quantum Tunneling of fields, esp. my doubts.

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\section{Tunneling of Quantum field}

This part is particular hard for me. There are majorly three problems. The first
and most obvious one, is why do we require a "thin wall" approximation? Why is
this approximation physical?

The next problem is how is expansion of first order in $f$ will make the
following equation:
\begin{equation}
    m\partial^2_r \phi = -\frac{m}{r}\partial_r \phi +
    \partial_\phi\left(V(\phi)-f\phi\right)
\end{equation}
into a simplified form:
\begin{equation}
    m\partial^2_r \phi = \partial_\phi(\phi)
\end{equation}

The last problem is that, the action in the new coordinate is:
\begin{equation}
    \int_0^{r_0}\dd{r} \int_0^{2\pi}\dd{\theta} \left[
        m(\partial_r\phi)^2+V(\phi)-f\phi\right] r
\end{equation}
where I have ignored several constants, and have used the formula:
\begin{equation}
    \dd{\tau}\dd{x} = r\dd{r}\dd{\theta}
\end{equation}
For the moment ignores $-f\phi r$, the first two terms:
\begin{equation}
    \int_0^{2\pi}\dd{\theta} \int_0^{r_0}\dd{r} \left[
        m(\partial_r\phi)^2 + V(\phi)
    \right] r
\end{equation}
is still one step away from producing a $S_{\text{inst}}$ term:
\begin{equation}
    S_{\text{inst}} := \int_0^T \dd{\tau} 
    \left(\frac{m}{2}(\partial_\tau\phi)^2 + V(\phi)\right)
\end{equation}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
